Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-17 graph_housing_exp2_distr_8_5.tex
Experiment part

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0000) (1.9204,0.3850,0.0000) (1.9204,0.4405,0.0000) (1.1296,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4405,0.0000) (1.9204,0.4405,0.0000) (1.9204,0.4860,0.0000) (1.1296,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4860,0.0000) (1.9204,0.4860,0.0000) (1.9204,0.4910,0.0000) (1.1296,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (1.9204,0.4910,0.0000) (1.9204,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (1.9204,0.4960,0.0000) (1.9204,0.5190,0.0000) (1.1296,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5190,0.0000) (1.9204,0.5190,0.0000) (1.9204,0.5220,0.0000) (1.1296,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5220,0.0000) (1.9204,0.5220,0.0000) (1.9204,0.5280,0.0000) (1.1296,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5280,0.0000) (1.9204,0.5280,0.0000) (1.9204,0.5410,0.0000) (1.1296,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0000) (1.9204,0.5410,0.0000) (1.9204,0.5455,0.0000) (1.1296,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5455,0.0025) (1.9204,0.5455,0.0025) (1.9204,0.5910,0.0025) (1.1296,0.5910,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5910,0.0425) (1.9204,0.5910,0.0425) (1.9204,0.6390,0.0425) (1.1296,0.6390,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0065) (1.9204,0.6390,0.0065) (1.9204,0.6510,0.0065) (1.1296,0.6510,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1040) (1.9204,0.6510,0.1040) (1.9204,0.8205,0.1040) (1.1296,0.8205,0.1040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0300) (1.9204,0.8205,0.0300) (1.9204,0.8710,0.0300) (1.1296,0.8710,0.0300)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.3850,0.0000) (2.5884,0.3850,0.0000) (2.5884,0.4405,0.0000) (1.9204,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4405,0.0000) (2.5884,0.4405,0.0000) (2.5884,0.4860,0.0000) (1.9204,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4860,0.0000) (2.5884,0.4860,0.0000) (2.5884,0.4910,0.0000) (1.9204,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.9204,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5190,0.0000) (1.9204,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5190,0.0085) (2.5884,0.5190,0.0085) (2.5884,0.5220,0.0085) (1.9204,0.5220,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5220,0.0000) (2.5884,0.5220,0.0000) (2.5884,0.5280,0.0000) (1.9204,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5280,0.0000) (2.5884,0.5280,0.0000) (2.5884,0.5410,0.0000) (1.9204,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5410,0.0025) (2.5884,0.5410,0.0025) (2.5884,0.5455,0.0025) (1.9204,0.5455,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5455,0.0580) (2.5884,0.5455,0.0580) (2.5884,0.5910,0.0580) (1.9204,0.5910,0.0580)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.5910,0.0485) (2.5884,0.5910,0.0485) (2.5884,0.6390,0.0485) (1.9204,0.6390,0.0485)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6390,0.0120) (2.5884,0.6390,0.0120) (2.5884,0.6510,0.0120) (1.9204,0.6510,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.6510,0.0665) (2.5884,0.6510,0.0665) (2.5884,0.8205,0.0665) (1.9204,0.8205,0.0665)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.9204,0.8205,0.0000) (2.5884,0.8205,0.0000) (2.5884,0.8710,0.0000) (1.9204,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0000) (3.0793,0.3850,0.0000) (3.0793,0.4405,0.0000) (2.5884,0.4405,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4405,0.0000) (3.0793,0.4405,0.0000) (3.0793,0.4860,0.0000) (2.5884,0.4860,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4860,0.0115) (3.0793,0.4860,0.0115) (3.0793,0.4910,0.0115) (2.5884,0.4910,0.0115)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0000) (3.0793,0.4910,0.0000) (3.0793,0.4960,0.0000) (2.5884,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0160) (3.0793,0.4960,0.0160) (3.0793,0.5190,0.0160) (2.5884,0.5190,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5190,0.0065) (3.0793,0.5190,0.0065) (3.0793,0.5220,0.0065) (2.5884,0.5220,0.0065)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5220,0.0000) (3.0793,0.5220,0.0000) (3.0793,0.5280,0.0000) (2.5884,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5280,0.0000) (3.0793,0.5280,0.0000) (3.0793,0.5410,0.0000) (2.5884,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0040) (3.0793,0.5410,0.0040) (3.0793,0.5455,0.0040) (2.5884,0.5455,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5455,0.0250) (3.0793,0.5455,0.0250) (3.0793,0.5910,0.0250) (2.5884,0.5910,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5910,0.0000) (3.0793,0.5910,0.0000) (3.0793,0.6390,0.0000) (2.5884,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0000) (3.0793,0.6390,0.0000) (3.0793,0.6510,0.0000) (2.5884,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0250) (3.0793,0.6510,0.0250) (3.0793,0.8205,0.0250) (2.5884,0.8205,0.0250)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (3.0793,0.8205,0.0000) (3.0793,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.3850,0.0100) (4.4802,0.3850,0.0100) (4.4802,0.4405,0.0100) (3.0793,0.4405,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4405,0.0495) (4.4802,0.4405,0.0495) (4.4802,0.4860,0.0495) (3.0793,0.4860,0.0495)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4860,0.0345) (4.4802,0.4860,0.0345) (4.4802,0.4910,0.0345) (3.0793,0.4910,0.0345)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4910,0.0000) (4.4802,0.4910,0.0000) (4.4802,0.4960,0.0000) (3.0793,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.4960,0.0425) (4.4802,0.4960,0.0425) (4.4802,0.5190,0.0425) (3.0793,0.5190,0.0425)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5190,0.0000) (4.4802,0.5190,0.0000) (4.4802,0.5220,0.0000) (3.0793,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5220,0.0000) (4.4802,0.5220,0.0000) (4.4802,0.5280,0.0000) (3.0793,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5280,0.0525) (4.4802,0.5280,0.0525) (4.4802,0.5410,0.0525) (3.0793,0.5410,0.0525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5410,0.0155) (4.4802,0.5410,0.0155) (4.4802,0.5455,0.0155) (3.0793,0.5455,0.0155)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5455,0.0135) (4.4802,0.5455,0.0135) (4.4802,0.5910,0.0135) (3.0793,0.5910,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.5910,0.0000) (4.4802,0.5910,0.0000) (4.4802,0.6390,0.0000) (3.0793,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6390,0.0000) (4.4802,0.6390,0.0000) (4.4802,0.6510,0.0000) (3.0793,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.6510,0.0000) (4.4802,0.6510,0.0000) (4.4802,0.8205,0.0000) (3.0793,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.0793,0.8205,0.0000) (4.4802,0.8205,0.0000) (4.4802,0.8710,0.0000) (3.0793,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.3850,0.0080) (4.7503,0.3850,0.0080) (4.7503,0.4405,0.0080) (4.4802,0.4405,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4405,0.0035) (4.7503,0.4405,0.0035) (4.7503,0.4860,0.0035) (4.4802,0.4860,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4860,0.0000) (4.7503,0.4860,0.0000) (4.7503,0.4910,0.0000) (4.4802,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4910,0.0100) (4.7503,0.4910,0.0100) (4.7503,0.4960,0.0100) (4.4802,0.4960,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.4960,0.0000) (4.7503,0.4960,0.0000) (4.7503,0.5190,0.0000) (4.4802,0.5190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5190,0.0000) (4.7503,0.5190,0.0000) (4.7503,0.5220,0.0000) (4.4802,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5220,0.0000) (4.7503,0.5220,0.0000) (4.7503,0.5280,0.0000) (4.4802,0.5280,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5280,0.0060) (4.7503,0.5280,0.0060) (4.7503,0.5410,0.0060) (4.4802,0.5410,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5410,0.0000) (4.7503,0.5410,0.0000) (4.7503,0.5455,0.0000) (4.4802,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5455,0.0000) (4.7503,0.5455,0.0000) (4.7503,0.5910,0.0000) (4.4802,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.5910,0.0000) (4.7503,0.5910,0.0000) (4.7503,0.6390,0.0000) (4.4802,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6390,0.0000) (4.7503,0.6390,0.0000) (4.7503,0.6510,0.0000) (4.4802,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.6510,0.0000) (4.7503,0.6510,0.0000) (4.7503,0.8205,0.0000) (4.4802,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.4802,0.8205,0.0000) (4.7503,0.8205,0.0000) (4.7503,0.8710,0.0000) (4.4802,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.3850,0.1860) (12.1265,0.3850,0.1860) (12.1265,0.4405,0.1860) (4.7503,0.4405,0.1860)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4405,0.0615) (12.1265,0.4405,0.0615) (12.1265,0.4860,0.0615) (4.7503,0.4860,0.0615)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4860,0.0000) (12.1265,0.4860,0.0000) (12.1265,0.4910,0.0000) (4.7503,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4910,0.0045) (12.1265,0.4910,0.0045) (12.1265,0.4960,0.0045) (4.7503,0.4960,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.4960,0.0210) (12.1265,0.4960,0.0210) (12.1265,0.5190,0.0210) (4.7503,0.5190,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5190,0.0000) (12.1265,0.5190,0.0000) (12.1265,0.5220,0.0000) (4.7503,0.5220,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5220,0.0120) (12.1265,0.5220,0.0120) (12.1265,0.5280,0.0120) (4.7503,0.5280,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5280,0.0000) (12.1265,0.5280,0.0000) (12.1265,0.5410,0.0000) (4.7503,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5455,0.0000) (4.7503,0.5455,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5455,0.0000) (12.1265,0.5455,0.0000) (12.1265,0.5910,0.0000) (4.7503,0.5910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.5910,0.0000) (12.1265,0.5910,0.0000) (12.1265,0.6390,0.0000) (4.7503,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.7503,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.7503,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.7503,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.7503,0.8710,0.0000)};

>>>>

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0060) (2.5884,0.3850,0.0060) (2.5884,0.4460,0.0060) (1.1296,0.4460,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4460,0.0000) (2.5884,0.4460,0.0000) (2.5884,0.4485,0.0000) (1.1296,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4485,0.0000) (2.5884,0.4485,0.0000) (2.5884,0.4555,0.0000) (1.1296,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4555,0.0000) (2.5884,0.4555,0.0000) (2.5884,0.4620,0.0000) (1.1296,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4620,0.0025) (2.5884,0.4620,0.0025) (2.5884,0.4705,0.0025) (1.1296,0.4705,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4705,0.0040) (2.5884,0.4705,0.0040) (2.5884,0.4910,0.0040) (1.1296,0.4910,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5015,0.0000) (1.1296,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5015,0.0000) (2.5884,0.5015,0.0000) (2.5884,0.5085,0.0000) (1.1296,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5085,0.0000) (2.5884,0.5085,0.0000) (2.5884,0.5165,0.0000) (1.1296,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5165,0.0215) (2.5884,0.5165,0.0215) (2.5884,0.5410,0.0215) (1.1296,0.5410,0.0215)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0055) (2.5884,0.5410,0.0055) (2.5884,0.5485,0.0055) (1.1296,0.5485,0.0055)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5485,0.0070) (2.5884,0.5485,0.0070) (2.5884,0.5775,0.0070) (1.1296,0.5775,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5775,0.0645) (2.5884,0.5775,0.0645) (2.5884,0.6010,0.0645) (1.1296,0.6010,0.0645)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6010,0.0260) (2.5884,0.6010,0.0260) (2.5884,0.6070,0.0260) (1.1296,0.6070,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6070,0.0085) (2.5884,0.6070,0.0085) (2.5884,0.6115,0.0085) (1.1296,0.6115,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6115,0.0100) (2.5884,0.6115,0.0100) (2.5884,0.6190,0.0100) (1.1296,0.6190,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6190,0.0325) (2.5884,0.6190,0.0325) (2.5884,0.6275,0.0325) (1.1296,0.6275,0.0325)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6275,0.0060) (2.5884,0.6275,0.0060) (2.5884,0.6390,0.0060) (1.1296,0.6390,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0210) (2.5884,0.6390,0.0210) (2.5884,0.6510,0.0210) (1.1296,0.6510,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1560) (2.5884,0.6510,0.1560) (2.5884,0.8205,0.1560) (1.1296,0.8205,0.1560)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0370) (2.5884,0.8205,0.0370) (2.5884,0.8710,0.0370) (1.1296,0.8710,0.0370)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0775) (4.9150,0.3850,0.0775) (4.9150,0.4460,0.0775) (2.5884,0.4460,0.0775)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4460,0.0150) (4.9150,0.4460,0.0150) (4.9150,0.4485,0.0150) (2.5884,0.4485,0.0150)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4485,0.0050) (4.9150,0.4485,0.0050) (4.9150,0.4555,0.0050) (2.5884,0.4555,0.0050)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4555,0.0040) (4.9150,0.4555,0.0040) (4.9150,0.4620,0.0040) (2.5884,0.4620,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4620,0.0080) (4.9150,0.4620,0.0080) (4.9150,0.4705,0.0080) (2.5884,0.4705,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4705,0.0290) (4.9150,0.4705,0.0290) (4.9150,0.4910,0.0290) (2.5884,0.4910,0.0290)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0095) (4.9150,0.4910,0.0095) (4.9150,0.4960,0.0095) (2.5884,0.4960,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0025) (4.9150,0.4960,0.0025) (4.9150,0.5015,0.0025) (2.5884,0.5015,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5015,0.0410) (4.9150,0.5015,0.0410) (4.9150,0.5085,0.0410) (2.5884,0.5085,0.0410)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5085,0.0100) (4.9150,0.5085,0.0100) (4.9150,0.5165,0.0100) (2.5884,0.5165,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5165,0.0605) (4.9150,0.5165,0.0605) (4.9150,0.5410,0.0605) (2.5884,0.5410,0.0605)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0295) (4.9150,0.5410,0.0295) (4.9150,0.5485,0.0295) (2.5884,0.5485,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5485,0.0095) (4.9150,0.5485,0.0095) (4.9150,0.5775,0.0095) (2.5884,0.5775,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5775,0.0105) (4.9150,0.5775,0.0105) (4.9150,0.6010,0.0105) (2.5884,0.6010,0.0105)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6010,0.0000) (4.9150,0.6010,0.0000) (4.9150,0.6070,0.0000) (2.5884,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6070,0.0000) (4.9150,0.6070,0.0000) (4.9150,0.6115,0.0000) (2.5884,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6115,0.0020) (4.9150,0.6115,0.0020) (4.9150,0.6190,0.0020) (2.5884,0.6190,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6190,0.0000) (4.9150,0.6190,0.0000) (4.9150,0.6275,0.0000) (2.5884,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6275,0.0020) (4.9150,0.6275,0.0020) (4.9150,0.6390,0.0020) (2.5884,0.6390,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0015) (4.9150,0.6390,0.0015) (4.9150,0.6510,0.0015) (2.5884,0.6510,0.0015)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0295) (4.9150,0.6510,0.0295) (4.9150,0.8205,0.0295) (2.5884,0.8205,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (4.9150,0.8205,0.0000) (4.9150,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.3850,0.1245) (12.1265,0.3850,0.1245) (12.1265,0.4460,0.1245) (4.9150,0.4460,0.1245)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4460,0.0135) (12.1265,0.4460,0.0135) (12.1265,0.4485,0.0135) (4.9150,0.4485,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4485,0.0160) (12.1265,0.4485,0.0160) (12.1265,0.4555,0.0160) (4.9150,0.4555,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4555,0.0090) (12.1265,0.4555,0.0090) (12.1265,0.4620,0.0090) (4.9150,0.4620,0.0090)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4620,0.0120) (12.1265,0.4620,0.0120) (12.1265,0.4705,0.0120) (4.9150,0.4705,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4705,0.0185) (12.1265,0.4705,0.0185) (12.1265,0.4910,0.0185) (4.9150,0.4910,0.0185)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4910,0.0030) (12.1265,0.4910,0.0030) (12.1265,0.4960,0.0030) (4.9150,0.4960,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4960,0.0070) (12.1265,0.4960,0.0070) (12.1265,0.5015,0.0070) (4.9150,0.5015,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5015,0.0000) (12.1265,0.5015,0.0000) (12.1265,0.5085,0.0000) (4.9150,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5085,0.0200) (12.1265,0.5085,0.0200) (12.1265,0.5165,0.0200) (4.9150,0.5165,0.0200)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5165,0.0160) (12.1265,0.5165,0.0160) (12.1265,0.5410,0.0160) (4.9150,0.5410,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5485,0.0000) (4.9150,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5485,0.0060) (12.1265,0.5485,0.0060) (12.1265,0.5775,0.0060) (4.9150,0.5775,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5775,0.0000) (12.1265,0.5775,0.0000) (12.1265,0.6010,0.0000) (4.9150,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6010,0.0000) (12.1265,0.6010,0.0000) (12.1265,0.6070,0.0000) (4.9150,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6070,0.0000) (12.1265,0.6070,0.0000) (12.1265,0.6115,0.0000) (4.9150,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6115,0.0000) (12.1265,0.6115,0.0000) (12.1265,0.6190,0.0000) (4.9150,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6190,0.0000) (12.1265,0.6190,0.0000) (12.1265,0.6275,0.0000) (4.9150,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6275,0.0000) (12.1265,0.6275,0.0000) (12.1265,0.6390,0.0000) (4.9150,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.9150,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.9150,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.9150,0.8710,0.0000)};
